\documentclass[10pt, letter]{article}

\input{formatting.tex}
\input{macros.tex}

\begin{document}


\handout{Rutgers ECE}{2022}{\textcolor{red}{your name here}}{\textcolor{red}{date of meeting}}{Post-Meeting Research Plan}

\noindent \textit{Try to fill out this form as soon as you can after having a research meeting. It is designed to help you process the discussion and plan and prioritize your work for the next week. Examples are given in the template so have a sense of what kinds of things to write.}


\subsubsection*{What new things did I learn from this meeting?}

\begin{note}
\begin{itemize}
\item Papers on XXX (e.g. ``eigenvalues of random matrices'') may relate to my problem.
\item My simulation results are probably not a bug but instead bad parameter choices.
\item There is a conference deadline in October that we can maybe plan for.
\end{itemize}
\end{note}


\subsubsection*{What are my new goals for this week?}

\textit{SMART is common acronym for talking about goals: Specific, Measurable, Achievable, Relevant, and Time-Bound.}

\begin{note}
	\begin{enumerate}
	\item Watch video lectures to get a basic understanding of RMT.
	\item Download and look at references on Matrix Bernstein inequalities used for compressed sensing 
	\item See if existing results apply to my problem and if not, why not.
	\item Search for a better parameters in the simulation.
	\item Download the paper template for the conference and check due dates.
	\end{enumerate}
\textbf{Schedule:} 1 = M-Th, 2 = W, 3 = F, 4 = T-W, 5 = M
\end{note}


\subsubsection*{What references/papers should I look at?}

\textit{You should be looking at (new) paper(s) every week in order to become an expert. Get in the habit!}

\begin{note}
\begin{itemize}
\item There's video lectures by Dumitriu on random matrix theory (RMT) on YouTube and some course notes.
\item Do a literature search on matrix concentration for compressed sensing.
\end{itemize}
\end{note}

\subsubsection*{What are the medium-term goals?}  

\textit{It's always good to keep the bigger picture in mind.}

\begin{note}
\begin{itemize}
\item Finish this proof by the end of the month.
\item Schedule a qualifying exam for next semester.
\item Get a draft/outline of a conference paper in the next two weeks.
\end{itemize}
\end{note}

\subsubsection*{How can I change the way I work?}

\textit{Reflecting on what worked/didn't work can help you find \textbf{your} best way of working.}

\begin{note}
\begin{itemize}
\item Make sure to not work on just one thing all day -- break it up a little.
\item Take written notes on papers as I read them instead of just reading them.
\item More comments in my code for simulations.
\end{itemize}
\end{note}

\subsubsection*{What was helpful or unhelpful in today's meeting?}

\textit{If you identify how a meeting can be more helpful, we structure future meetings better.}

\begin{note}
\begin{itemize}
\item Getting specific words to search for in Google Scholar was nice.
\item Spending a few minutes at the end to recap helped clarify things.
\item Reading through my code to debug during the meeting was not a good use of time.
\item I felt like I didn't know what was expected of me.
\end{itemize}
\end{note}


\subsubsection*{Additional comments}

\begin{note}
It would help to end 5 minutes early so I have time to go to my class.
\end{note}


\end{document}
